Polarized Illumination For Determining Single-Molecule Orientation: Modeling and Design Comparison

### 2017-07-07 paper/paper/paper.tex
Generate and caption single frame figure.

\documentclass[10pt]{article}
\usepackage[OE]{express}

\begin{document}
\title{Polarized Illumination For Determining Single-Molecule Orientation:
  Modeling and Instrument Design}

\author{Talon Chandler,\authormark{1} Author Two,\authormark{2,*} and Author Three\authormark{2,3}}

\address{\authormark{1}Peer Review, Publications Department, The Optical Society, 2010 Massachusetts Avenue NW, Washington, DC 20036, USA\\
\authormark{2}Publications Department, The Optical Society, 2010 Massachusetts Avenue NW, Washington, DC 20036, USA\\
\authormark{3}Currently with the Department of Electronic Journals, The Optical Society, 2010 Massachusetts Avenue NW, Washington, DC 20036, USA}

\email{talonchandler@talonchandler.com} %% email address is required

@@

We propose polarized illumination as an complementary method to polarized
detection. We get the speed (no shape analysis required).

@@

\section{Methods}
\subsection{Illumination Model}

\subsection{Detection Model}

@@

\subsection{Microscope Designs}

\subsection{Evaluation Metrics}
\begin{align}
  F &= \sum_{i=0}^N \frac{1}{I}
  \begin{bmatrix}
    \frac{\partial^2 I}{\partial \Theta^2}&\frac{\partial I}{\partial \Theta}\frac{\partial I}{\partial \Phi}\\
    \frac{\partial I}{\partial \Theta}\frac{\partial I}{\partial \Phi}&\frac{\partial^2 I}{\partial \Phi^2}\\    
  \end{bmatrix}\\
  \sigma_{\Omega} &= \frac{\sin\Theta}{\sqrt{\text{det}\{F\}}}
\end{align}
We call $\sigma_{\Omega}$ the \emph{solid-angle uncertainty}. 
We sampled $\sigma_{\Omega}$ on 100,000 approximately equally
spaced points on the unit sphere and calculated the \emph{coefficient of variation}
$c_v$ of these points where
\begin{align}
  c_v = \frac{\sigma_{\sigma_{\Omega}}}{\mu_{\sigma_{\Omega}}}
\end{align}

\section{Results}
\subsection{One-Arm Designs}
\begin{figure}[htbp]
\centering\includegraphics[width=\textwidth]{single-arm}
\caption{\textbf{Left:} Schematic of a single-arm four-frame epi-illumination
  microscope with NA = 0.8 and $n = 1.33$. The solid and dashed lines enclose
  the illumination and detection solid angles, respectively, and the arrows
  indicate the illumination polarization orientations. \textbf{Right:} Solid
  angle uncertainty for the same microscope when $I_{\text{tot}} = 1000$
  photons. Note the regions of high uncertainty near the equator and poles
  as noted in XXX.}
\end{figure}

\subsection{Two-Arm Designs}
\subsection{Three-Arm Designs}

@@

\section*{Acknowledgments}
TODO

>>>>

\documentclass[10pt]{article}
\usepackage[OE]{express}
\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}} 
\providecommand{\mb}[1]{\mathbf{#1}}
\providecommand{\mh}[1]{\mathbf{\hat{#1}}}
\providecommand{\bs}[1]{\boldsymbol{#1}} 
\providecommand{\intinf}{\int_{-\infty}^{\infty}}

\begin{document}
\title{Polarized Illumination For Determining Single-Molecule Orientation:
  Modeling and Design Comparison}

\author{Talon Chandler,\authormark{1,*} Shalin Mehta,\authormark{2} Rudolf Oldenbourg,\authormark{2, 3} and Patrick J. La Rivi\`ere\authormark{1}}

\address{\authormark{1}University of Chicago, Department of Radiology, Chicago, IL, USA.\\
\authormark{2}Marine Biological Laboratory, Bell Center for Regenerative Medicine, Woods Hole, MA, USA.\\
\authormark{3}Brown University, Department of Physics, Providence, RI, USA.}
\email{*talonchandler@talonchandler.com} %% email address is required

@@

We propose polarized illumination as an complementary method to polarized
detection. We get the speed (no shape analysis required). We don't waste any
dose (polarized light throws away light dose).

@@

\section{Methods}
\subsection{Illumination Model}
\begin{align}
  \eta_{\text{det},\phi_{\text{det}}}  = \frac{\int_{\Omega}d\mh{r}\ \left|\mh{P}_{\text{det}}\cdot\tilde{\mb{R}}(\mh{r})(\mh{r}\times\hat{\bs{\mu}}_{\text{em}}\times\mh{r})\right|^2}{\int_{\mathbb{S}^2}d\mh{r}\left|\mh{r}\times\hat{\bs{\mu}}_{\text{em}}\times\mh{r}\right|^2}\label{eq:final}
\end{align}
where
\begin{align}
  \hat{\mb{r}} &= \sin\theta\cos\phi\hat{\mb{i}} + \sin\theta\sin\phi\hat{\mb{j}} + \cos\theta\hat{\mb{k}}\label{eq:r_coords}\ \ \ \text{is the dummy integration vector,}\\
  \hat{\bs{\mu}}_{\text{em}} &= \sin\Theta\cos\Phi\hat{\mb{i}} + \sin\Theta\sin\Phi\hat{\mb{j}} + \cos\Theta\hat{\mb{k}}\ \ \ \text{is the emission dipole moment,}\label{eq:mu_coords}\\
  \tilde{\mb{R}}(\mh{r}) &= \begin{bmatrix} \cos\theta\cos^2\phi + \sin^2\phi & (\cos\theta -1)\sin\phi\cos\phi & -\sin\theta\cos\phi\\ (\cos\theta - 1)\sin\phi\cos\phi & \cos\theta\sin^2\phi + \cos^2\phi & -\sin\theta\sin\phi \\ \sin\theta\cos\phi& \sin\theta\sin\phi & \cos\theta \end{bmatrix}\label{eq:matrix}\\&\text{is the rotation matrix that models the objective lens,}\\
  \hat{\mb{P}}_{\text{det}} &= \cos\phi_{\text{det}}\hat{\mb{i}} + \sin\phi_{\text{det}}\hat{\mb{j}}\ \ \ \text{is the pass axis of the polarizer,}\\
  \Omega &= \{(\phi, \theta)|\phi \in (0,2\pi]\ \text{and}\ \theta\in (0, \alpha]\}\ \ \ \text{is the cap of the sphere collected by the objective.}
\end{align}

\begin{align}
  \eta_{\text{exc},\phi_{\text{pol}}}(\Theta, \Phi, \alpha) &= D\{A + B\sin^{2}{\Theta} + C\sin^{2}{\Theta} \cos{[2 (\Phi - \phi_{\text{pol}}})]\}.
\end{align}
\begin{subequations}
\begin{align}
  A &= \frac{1}{4} - \frac{3}{8} \cos{\alpha } + \frac{1}{8} \cos^{3}{\alpha }\\
  B &= \frac{3}{16} \cos{\alpha } - \frac{3}{16} \cos^{3}{\alpha }\\
  C &= \frac{7}{32} - \frac{3}{32} \cos{\alpha } - \frac{3}{32} \cos^{2}{\alpha } - \frac{1}{32} \cos^{3}{\alpha}\\
  D &= \frac{4}{3(1 - \cos\alpha)}.
\end{align}%
\end{subequations}

\subsection{Detection Model}
\begin{align}
  \eta_{\text{det}}(\Theta, \alpha) = 2(A + B\sin^2\Theta)
\end{align}

@@

\begin{figure}[htbp]
\centering\includegraphics[width=\textwidth]{single-frame}
\caption{Representative examples of the forward model for single frame
  microscopes.\newline \newline \textbf{Columns left to right:} (1) schematics of
  single frame microscopes where the solid line encloses the illumination
  solid angle, the dashed line encloses the detection solid angle, and the arrow
  indicates the transmission axis of the illumination polarizer; (2) the excitation
  efficiency see equation XX; (3) the detection efficiency see equation X; (4)
  the total efficiency see equation X.\newline \newline \textbf{Rows top to
    bottom:} (1) epi-illumination (NA = 1.1) with $x$-polarized light and
  epi-detection (NA = 1.1); (2) orthogonal illumination (NA = 0.8) and detection
  (NA = 0.8); (3) oblique illumination (NA = 0.8) and detection (NA = 0.8).}
\end{figure}

\subsection{Microscope Designs}
Widefield illumination vs light sheet illumination.

- Light sheet has low illumination. 
- Restricted to orthogonal detection.

\subsection{Evaluation Metrics}
\begin{align}
  F &= \sum_{i=0}^N \frac{1}{I}
  \begin{bmatrix}
    \frac{\partial I}{\partial \Theta}\frac{\partial I}{\partial \Theta}&\frac{\partial I}{\partial \Theta}\frac{\partial I}{\partial \Phi}\\\\
    \frac{\partial I}{\partial \Theta}\frac{\partial I}{\partial \Phi}&\frac{\partial I}{\partial \Phi}\frac{\partial I}{\partial \Phi}\\    
  \end{bmatrix}\\
  \sigma_{\Omega} &= \frac{\sin\Theta}{\sqrt{\text{det}\{F\}}}
\end{align}
We call $\sigma_{\Omega}$ the \emph{solid-angle uncertainty}. 
We sampled $\sigma_{\Omega}$ on 100,000 approximately equally
spaced points on the unit sphere and calculated the \emph{coefficient of variation}
$c_v$ of these points where
\begin{align}
  c_v = \frac{\sigma_{\sigma_{\Omega}}}{\mu_{\sigma_{\Omega}}}
\end{align}

\section{Results}
\subsection{One-Arm Designs}
\begin{figure}[htbp]
\centering\includegraphics[width=\textwidth]{single-arm}
\caption{\textbf{Left:} Schematic of a single-arm four-frame epi-illumination
  microscope with NA = 0.8 and $n = 1.33$.  \textbf{Right:} Solid
  angle uncertainty for the same microscope when $I_{\text{tot}} = 1000$
  photons. Note the regions of high uncertainty near the equator and poles
  as noted in XXX.}
\end{figure}

Can't use $c_v$ because it doesn't converge.

High variance around equator and poles.

\subsection{Two-Arm Designs}
Widefield vs light sheet.

Widefield NA vs angle/.

Sweep asymmetry for full NA light sheet.

\subsection{Three-Arm Designs}

@@

\section*{Acknowledgments}
We thank Hari Shroff and Sean Rose for helpful conversations.
